\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Database Requirements for Twitter Clone Project (Using Supabase)}
\author{}
\date{}

\begin{document}

\maketitle

\section{Database Requirements}

We are utilizing Supabase as our database solution for the Twitter clone project. Below are the database requirements:

\subsection{Tables}

\subsubsection{Comments}
\begin{itemize}
    \item id: Unique identifier for each comment.
    \item tweet\_id: Foreign key referencing the tweet on which the comment was made.
    \item user\_id: Foreign key referencing the user who posted the comment.
    \item content: Text content of the comment.
    \item created\_at: Timestamp indicating when the comment was posted.
\end{itemize}

\subsubsection{Followers}
\begin{itemize}
    \item id: Unique identifier for each follower relationship.
    \item follower\_id: Foreign key referencing the user who is following.
    \item following\_id: Foreign key referencing the user who is being followed.
    \item created\_at: Timestamp indicating when the following relationship was established.
\end{itemize}

\subsubsection{Likes}
\begin{itemize}
    \item id: Unique identifier for each like.
    \item tweet\_id: Foreign key referencing the tweet that was liked.
    \item user\_id: Foreign key referencing the user who liked the tweet.
    \item created\_at: Timestamp indicating when the like was given.
\end{itemize}

\subsubsection{Notification Types}
\begin{itemize}
    \item id: Unique identifier for each notification type.
    \item name: Name or description of the notification type.
\end{itemize}

\subsubsection{Notifications}
\begin{itemize}
    \item id: Unique identifier for each notification.
    \item user\_id: Foreign key referencing the user who received the notification.
    \item type\_id: Foreign key referencing the type of notification.
    \item content: Text content of the notification.
    \item created\_at: Timestamp indicating when the notification was sent.
\end{itemize}

\subsubsection{Profile}
\begin{itemize}
    \item id: Unique identifier for each user profile.
    \item user\_id: Foreign key referencing the user.
    \item bio: Biography or description of the user.
    \item location: Location of the user.
    \item website: Website URL of the user.
    \item created\_at: Timestamp indicating when the profile was created.
\end{itemize}

\subsubsection{Retweets}
\begin{itemize}
    \item id: Unique identifier for each retweet.
    \item tweet\_id: Foreign key referencing the original tweet being retweeted.
    \item user\_id: Foreign key referencing the user who retweeted the tweet.
    \item created\_at: Timestamp indicating when the retweet was made.
\end{itemize}

\subsubsection{Saves}
\begin{itemize}
    \item id: Unique identifier for each saved tweet.
    \item tweet\_id: Foreign key referencing the tweet being saved.
    \item user\_id: Foreign key referencing the user who saved the tweet.
    \item created\_at: Timestamp indicating when the tweet was saved.
\end{itemize}

\subsubsection{Tweets}
\begin{itemize}
    \item id: Unique identifier for each tweet.
    \item user\_id: Foreign key referencing the user who posted the tweet.
    \item imgUrl: URL link that references the image that's attached to the tweet.
    \item likeCount : Number of likes the tweet received.
    \item retweetCount: Number of retweets the tweet received.
    \item tag: Other users that have been mentioned in the tweet.
    \item content: Text content of the tweet.
    \item created\_at: Timestamp indicating when the tweet was posted.
\end{itemize}

\subsubsection{User}
\begin{itemize}
    \item id: Unique identifier for each user.
    \item username: Username chosen by the user (unique).
    \item email: Email address of the user (unique).
    \item password: Encrypted password of the user.
    \item created\_at: Timestamp indicating when the user account was created.
\end{itemize}
\subsection*{Tweet_Tags}
\begin{itemize}
    \item id: Unique identifier for each tag.
\end{itemize}
\subsection*{Stored_Tags}
\begin{itemize}
    \item id: Unique identifier for each tag.
\end{itemize}

\subsection*{Topics}
\begin{itemize}
    \item id: Unique identifier for each topic.
    \item name: Name of the topic.
\end{itemize}
\end{document}
